% !TEX root = LMEDS_manual.tex

%%%%%%%%%%%%%%%%%%%%%
\section{LMEDS change history}
%%%%%%%%%%%%%%%%%%%%%

November 2, 2016 - LMEDS 2.4

\begin{itemize}
\item Stimulus presentation can now be automatically randomized for each user
\begin{itemize}
\item Test post-processing scripts will unscramble the output while marking the order users did the task in.
\end{itemize}
\item Task timeout and media-less support added to media\_choice pages
\item A limit can be set on the minimum and maximum number of prominences and boundaries that can be made on a text in the boundary- and prominence-marking pages.
\item Keyboard keys can be bound to buttons on a page (e.g. the `p' button can be used to play audio or `enter' can be pressed to submit a response)
\item Numerous bugfixes and code cleanup.
\end{itemize}

May 17, 2016 - LMEDS 2.3

\begin{itemize}
\item Video now supported with the same controls and functionality as audio
\item User script utilities can now be run from a web browser for greater ease of use
\item Pages can now have sliding scales
\item New syllable-marking page (branch of prominence-marking pages)
\item Experiment participants can now relogin and resume from where they left off (if enabled by the experimenter)
\item Integration tests added for greater reliability.  Also, numerous bugfixes.
\end{itemize}

December 15, 2015 - LMEDS 2.2

\begin{itemize}
\item Added support for python 3.x (tested on 3.5)
\end{itemize}

September 2015 - LMEDS 2.1

\begin{itemize}
\item Substituted the many specific forced choice pages (same\_different, ab, axb, etc) with one new page: audio\_choice
\end{itemize}

August 2015 - LMEDS 2.0

\begin{itemize}
\item First public release.  
\item Inclusion of user script utilities.
\item Numerous bugfixes and stability improvements (audio is significantly less error prone).  
\item Offline server for running experiments locally.
\item Companion website.
\end{itemize}

May 2014 - LMEDS 1.5

\begin{itemize}
\item Object oriented refactor.
\item Numerous bugfixes and stability improvements.
\end{itemize}

November 2013 - LMEDS 1.0

\begin{itemize}
\item First official release.  
\item First official experiments run using LMEDS.
\end{itemize}

May 2013 - LMEDS 0.0

\begin{itemize}
\item Work begins on LMEDS
\end{itemize}


\section{LMEDS manual change history}

November 2, 2016

\begin{quote}
Updated the manual to be in line with changes from LMEDS 2.4.
\end{quote}

May 17, 2016

\begin{quote}
Updated the manual to be in line with changes from LMEDS 2.2 and 2.3.  Added the workflow schematic.  Clarified other parts of text.
\end{quote}

November 11, 2015

\begin{quote}
Updated the manual to be in line with changes from LMEDS 2.1.
\end{quote}

August 5, 2015

\begin{quote}
Second release.  Move from Word to LaTeX for easier tracking of changes.
\end{quote}

December 17, 2013


\begin{quote}
First release
\end{quote}


